\documentclass[12pt]{cornelltfpxsop}
\title{Gantry Maintenance\newline}
\date{\today}
\author{Jose Andres Monroy}
\approved{Jose Andres Monroy}
\sopid{GM}
\sopversion{v1}
\sopabstract{This document describes the regular maintenance for the gantry.}
\begin{document}

\maketitle

%------------------------------------------------------------------
\section{Scope}
This document describes the maintenance of the gantry.

%------------------------------------------------------------------
\section{Purpose}
The gantry is a crucial equipment for manufacturing DEEs and performing the module DEE-integration. This SOP describes the maintenance steps for keeping it in working condition.

%------------------------------------------------------------------
%\section{Definitions}

%------------------------------------------------------------------
\section{Responsibilities}
Every person operating the gantry is responsible to maintain it. While a minimum schedule for maintenance activities is outlined in this document, any person is allowed to trigger out-of-cycle maintenance if needed to maintain working conditions.

%------------------------------------------------------------------
\section{Equipment}

\begin{itemize}
    \item Isopropil Alcohol (IPA) Wipe pads, non-dusty tissues
    \item Grease, safe for cleanroom applications.

    There is a small tube in the cabinet, supplied by the manufacturer of the gantry. Only use grease recommended by the manufacturer.
\end{itemize}

% Consider adding images of key equipment if it helps

%------------------------------------------------------------------
\section{Procedure}

% Mention to record certain observations if this is needed
\subsection{Weekly maintenance}
\begin{enumerate}
    \item Clean the surface of the gantry and the tools mounted to it using IPA wiping pads.
    \item Remove any obvious dirt. In case of residues from epoxy and TIM deposition.
\end{enumerate}

\subsection{Monthly maintenance}
\begin{enumerate}
    \item Check the steel surface of the left rail. If it looks dry, apply a small amount of grease using a wiping pad.

    Note: Other rails do not need to be checked as they are not exposed like the left rail.
\end{enumerate}
No other maintenance is required. If the gantry is malfunctioning for no obvious reason, get in touch with the manufacturer (Aerotech).

%------------------------------------------------------------------
\section{Documentation}
The following information needs to be recorded in the report for the UNL logbook:
\begin{itemize}
    \item Date, time (start--end) and operator name.
    \item Any special observations, e.g.~any deviation from expectation.
    \item Any action taken.
\end{itemize}

\end{document}

